---
title: "Getting started with Coinmarketcapr"
author: "AbdulMajedRaja"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Put the title of your vignette here}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette is to help you get started with Coinmarketcapr Package that helps to extract and monitor price and market cap of Cryptocurrencies from 'CoinMarketCap' <https://coinmarketcap.com/api/>. Simply, Coinmarketcapr is an R-binding for Coinmarketcap API that lists Price, Marketcap, Transaction Volume of many Cryptocurrencies and tokens. This package contains three primary functions:

- `get_global_marketcap()`
- `get_marketcap_ticker_all()`
- `plot_top_5_currencies()`

## Getting Global Marketcap

This function `get_global_marketcap()`

## Plotting Top 5 Cryptocurrencies

This function `plot_top_5_currencies()` makes it straightforward to make a barplot of top 5 cryptocurrencies.
```{r, fig.show='hold', fig.cap='Plotting Top 5 Cryptocurrencies'}
library(coinmarketcapr)
plot_top_5_currencies()
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
