---
title: "Getting started with Coinmarketcapr"
author: "AbdulMajedRaja"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with Coinmarketcapr}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette is to help you get started with Coinmarketcapr Package that helps to extract and monitor price and market cap of Cryptocurrencies from **CoinMarketCap**. Simply, Coinmarketcapr is an R-binding for Coinmarketcap API that lists Price, Marketcap, Transaction Volume of many Cryptocurrencies and tokens. 

### Basic Functions 

This package contains three primary functions:

- `get_valid_currencies()`
- `get_global_marketcap()`
- `get_marketcap_ticker_all()`
- `plot_top_currencies()`

### Getting Valid Currrenices 

This function `get_valid_currencies()` lists a character vector with all the valid currencies (ISO Codes) supported by Coinmarketcap API. These currency codes can be used in other functions like `get_global_marketcap()` to extract values in the given currency. 

```{r}
library(coinmarketcapr)
get_valid_currencies()
```


### Getting Global Marketcap

This function `get_global_marketcap()` fetches the USD value of global marketcap of all cryptocurrencies.

```{r}
library(coinmarketcapr)
get_global_marketcap()
```

### Extracting all Cryptocurrencies 

This function `get_marketcap_ticker_all()` gets various useful values such as Price, Marketcap, Total Volume, 24-hour Change and much for all the cryptocurrencies. 

```{r}
library(coinmarketcapr)
names(get_marketcap_ticker_all())
```


### Plotting Top Cryptocurrencies

This function `plot_top_currencies()` makes it straightforward to make a barplot of top cryptocurrencies by their rank which is actually based on Market cap.

```{r, fig.cap='Plotting Top 5 Cryptocurrencies', fig.width=6, fig.height=6}
library(coinmarketcapr)
plot_top_currencies('USD',5)
```

### Plotting with Themes

`plot_top_currencies()` outputs a `ggplot` object hence using `+` operator a new ggplot2 theme can be applied. `ggthemes` package has got a rich set of out-of-box themes to use with. 


```{r, fig.cap='Plot with Themes', fig.width=6, fig.height=6}
library(ggthemes)
plot_top_currencies() + 
        theme_economist()
```

### Cryptocurrencies Market - Tidy Analysis

Since `coinmarketcapr`'s `get_marketcap_ticker_all()` returns a dataframe, it could be fit in alongside with Tidy Data pipeline. 

```{r, fig.cap='Cryptocurrencies Price in USD Histogram', fig.width=6, fig.height=6}
library(coinmarketcapr)
library(dplyr)
library(ggplot2)

get_marketcap_ticker_all() %>% 
        slice(1:30) %>% 
        mutate(price_usd = as.numeric(price_usd)) %>% 
        ggplot() + geom_histogram(aes(price_usd)) +
        ggtitle('Cryptocurrencies Price in USD Histogram')
```


### Courtesy

Coinmarketcapr is powered by Coinmarketcap.com <https://coinmarketcap.com/api/> 
