---
title: "Getting started with Coinmarketcapr"
author: "AbdulMajedRaja"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with Coinmarketcapr}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette is to help you get started with Coinmarketcapr Package that helps to extract and monitor price and market cap of Cryptocurrencies from **CoinMarketCap**. Simply, Coinmarketcapr is an R-binding for Coinmarketcap API that lists Price, Marketcap, Transaction Volume of many Cryptocurrencies and tokens. 

### Basic Functions 

This package contains three primary functions:

- `get_valid_currencies()`
- `get_global_marketcap()`
- `get_marketcap_ticker_all()`
- `plot_top_currencies()`

### Getting Valid Currrenices 

This function `get_valid_currencies()` lists a character vector with all the valid currencies (ISO Codes) supported by Coinmarketcap API. These currency codes can be used in other functions like `get_global_marketcap()` to extract values in the given currency. 

```{r}
library(coinmarketcapr)
get_valid_currencies()
```


### Getting Global Marketcap

This function `get_global_marketcap()` fetches the USD value of global marketcap of all cryptocurrenices.

```{r}
library(coinmarketcapr)
get_global_marketcap()
```

### Extracting all Cryptocurrenices 

This function `get_marketcap_ticker_all()` gets various useful values such as Price, Marketcap, Total Volume, 24-hour Change and much for all the cryptocurrencies. 

```{r}
library(coinmarketcapr)
names(get_marketcap_ticker_all())
```


### Plotting Top Cryptocurrencies

This function `plot_top_5_currencies()` makes it straightforward to make a barplot of top 5 cryptocurrencies.

```{r, fig.cap='Plotting Top 5 Cryptocurrencies', fig.width=6, fig.height=6}
library(coinmarketcapr)
plot_top_currencies()
```

### Courtesy

Coinmarketcapr is powered by Coinmarketcap.com <https://coinmarketcap.com/api/> 
